Automatic Matching of Bullet Lands

### 2016-04-19 imaging-paper.tex
added ccf to the list of features - where was that before??

\end{knitrout}
    }
\end{subfigure}
\caption{\label{fig:cross100}Signatures of bullets 1-5 and 2-1 taken at  heights of $x = 100\mu m$. A horizontal shift of the values of bullet~1-5 to the right shows the similarity of the striation marks.}
\end{figure}
%
This horizontal shift is based on the cross-correlation between the two signatures: let $f(t)$ and $g(t)$ define the signature values  at $t$, where $t$ are locations between 0~$\mu m$ and about 2500~$\mu m$, 1.5625~$\mu m$ apart.
The cross-correlation between $f$ and $g$ at lag $k$ is then defined as
\[
(f * g) (k) = \sum_t f(t+k) g(t),
\]
with suitably defined limits for the summation. % (because variances of $f$ and $g$ do not change, the above equation is proportional to the correlation).

>>>>

\end{knitrout}
    }
\end{subfigure}
\caption{\label{fig:cross100}Signatures of bullets 1-5 and 2-1 taken at  heights of $x = 100\mu m$. A horizontal shift of the values of bullet~1-5 to the right shows the similarity of the striation marks.}
\end{figure}
%
\hh{For this alignment we use the cross-correlation function to find a maximal amount of agreement between the signatures~\cite{bachrach:2002, vorburger:2011, thompson:2013}.}
This horizontal shift is based on the cross-correlation between the two signatures: let $f(t)$ and $g(t)$ define the signature values  at $t$, where $t$ are locations between 0~$\mu m$ and about 2500~$\mu m$, 1.5625~$\mu m$ apart.
The cross-correlation between $f$ and $g$ at lag $k$ is then defined as
\[
(f * g) (k) = \sum_t f(t+k) g(t),
\]
with suitably defined limits for the summation. % (because variances of $f$ and $g$ do not change, the above equation is proportional to the correlation).
